%!TEX TS-program = xelatex
\documentclass{article}
\usepackage{hyperref}

\usepackage{geometry}
\geometry{
  % showframe,            % visualize the document layout.
  letterpaper,            % US-letter ANSI A paper size (215.9x279.4 mm)
  textwidth  = 165.33mm,  % 15.11466 cm (default for
  textheight = 230.00mm   % BTA: textwidth * phi,  where phi = 1.618 golden ratio.
}


\title{\textbf{\Large BIOGRAPHICAL SKETCH \\ Baudilio Tejerina, Ph. D. \\ October 2020} \\
%%{\normalsize  \\
%%  University of Things, Town, Country \\
%%  bltejerina@noaa.gov}
}


\author{}
\date{}

\begin{document}

\maketitle
\thispagestyle{empty}
\pagestyle{plain}

\section*{Education and Training}
\begin{itemize}
\item Universidad de Oviedo, Chemistry B.S. 1987, Asturias, Spain
\item Universidad de Oviedo, Theoretical Chemistry M.S. 1993, Asturias, Spain
\item Universidad de Oviedo, Physical Chemistry Ph.D. 1999, Asturias, Spain
\item Iowa State University, Theoretical Chemistry, Post-Doc. 2004, Ames, IA
\item Purdue University, Visiting Scholar, Dpt. EECS, 2010, West Lafayette, IN
\item Texas Tech University, Visiting Scholar, Dpt. Physics, 2019, Lubbock, TX
\end{itemize}

\section*{Research and Professional Experience}
\begin{itemize}
\item 1994-96 Assistant, Associate Professor Chemistry, Universidad de Oviedo
\item 1997-99 Assistant, Associate Professor Chemistry, Universidad de Almer\'{i}a
\item 2000-04 Postdoctoral Research Fellow, Iowa State University, Ames Laboratory, Ames, IA
\item 2004-10 Scientific IT Director, Department of Chemistry, Northwester University, Evanston, IL
\item 2007-10 Scientific Site Lead NCN, Northwester University, Evanston, IL
\item 2010-12 Sr Research Associate, Non-Equilibrium Energy Research Center (NERC) US-DOE, Northwester University, Evanston, IL
\item 2011-11 Adjunct Professor of Chemistry, Roosevelt University, Chicago, IL
\item 2012-15 Scientific IT Consultant, Earth and Planetary Sciences, Northwester University, Evanston, IL
\item 2015-17 Software Developer, Bank of America - Merrill Lynch, Chicago, IL
\item 2017-18 Independent consultant, Software and Hardware Engineer, Evanston, IL
\item 2018-20 Sr Scientific Software Developer, Concentric Advisors Texas, Inc., Lubbock, TX
\item 2020--Present Sr High Performance Systems and Software Engineer, GFDL - NOAA, Princeton, NJ

\end{itemize}

\section*{Products}

\subsection*{Most recent peer-reviewed publications}

\begin{enumerate}

\item Ultrasensitive detection of toxic cations based on the tunneling current through films of \emph{striped} nanoparticles. Cho, E. S.; Kim, J.; \underline{Tejerina, B.}; Hermans, T. M.; Jiang, H.; Nakanishi, H.; Yu, M.; Patashinski, A. Z.; Glotzer, S. C.; Stellacci, F.; Grzybowski, B. A. \emph{Nature Chemistry} {\bf 2012} \emph{}, Accepted.

\item Molecular tethering or aggregation -- is the existence of charge transfer band indicative of a Blue-Box/TTF inclusion complex formation? \underline{Tejerina, B.}; Gothard, C. M.; Grzybowski, B. A. \emph{Chem. Eur. J.} {\bf 2012}, \emph{18}, 5606--5611.

\item Northwestern University Initiative for Teaching NanoSciences (NUITNS): An Approach for Teaching Computational Chemistry to Engineering Undergraduate Students. Simeon, T.; Aikens, C.; \underline{Tejerina, B.}; Schatz, G. \emph{J. Chem. Ed.} {\bf 2011}, \emph{88}, 1079--1084.

\item  Bridging Interactions and Selective Nanoparticle Aggregation Mediated by Monovalent Cations. Wang, D. W.;  \underline{Tejerina, B.}; Lagzi, I.; Kowalczyk, B.; Grzybowski, B. A. \emph{ACS Nano} {\bf 2011}, \emph{5}, 530--536.

 \item Addition of POSS--T8 to Si(100) surface.  \underline{Tejerina, B.}; Gordon, M.S. \emph{J. Phys. Chem. C} {\bf 2008}, \emph{112}, 754.
\end{enumerate}


\subsection*{Software publications}
\begin{enumerate}

\item \href{http://nanohub.org/tools/acmenpds}{ACMENPDS} \emph{Active Media Nanophotonics Device Simulator.} Tejerina B.; Zhang, Z.; Zheng, Y.; Ho, S.-T. \emph{NCN}, {\bf 2011}. Theoretical design of materials with specific optical properties. Graphical interface for input of the geometry of the devices and automatic 3D visualization of scalar and vector data.\\
\emph{Programming Languages}: Fortran-90, OpenMPI, TCL/TK.\\ (\href{http://www.nanohub.org/tools/acmenpds}{http://www.nanohub.org/tools/acmenpds})

\item \href{http://nanohub.org/tools/dpowj} {EPR/ESR} \emph{Calculation of the powder pattern EPR spectra of a 2-spin electronic system.} Tejerina, B.; Telser, J. \emph{NCN}, {\bf 2009}.  Simulation of the spectra of two interacting spin systems in a magnetic field.\\
\emph{Languages}: Fortran-90, TCL/TK.  -- (\href{http://nanohub.org/tools/dpowj}{http://nanohub.org/tools/dpowj})

\item \href{http://www.nanohub.org/tools/nuitns}{NUITNS} \emph{Northwestern University Initiative for Teaching Nanoscience.} Tejerina, B. \emph{NCN}, {\bf 2008}. Graphical interface for a suit of programs .\\
\emph{Languages}: C$++$, Fortran-90, TCL/TK, PovRay, XML, Perl.\\ (\href{http://www.nanohub.org/tools/nuitns}{http://www.nanohub.org/tools/nuitns})


\item \href{http://www.nanohub.org/tools/tedvis}{TEDVis} \emph{Theoretical Electron Density Visualizer.} Tejerina, B. \emph{NCN}, {\bf 2007}.  Topological analysis of molecular wave functions .\\
\emph{Languages}: Fortran-90, OpenMP-API. \\ (\href{http://www.nanohub.org/tools/tedvis}{http://www.nanohub.org/tools/tedvis})

\item \href{http://nanohub.org/tools/cgls} {CGLS} \emph{Coarse Grain Lipid Simulator: Modeling, construction and analysis of lipid systems.} Tejerina, B.; Brezinski, E.; McCullagh, M.; Schatz, G. \emph{NCN}, {\bf 2007}. Simulation of large biological systems (lipids) using Molecular Dynamics with coarse grain metod. \emph{Languages}: Fortran-90, Perl. \\ (\href{http://nanohub.org/tools/cgls}{http://nanohub.org/tools/cgls})

\end{enumerate}

%%Collaborator and coeditors,
%%
%%K12 Education adn curriculum Development
%%- Intitutos
%%- Radio
%%- Chicago public library.
%%- NSF REU Research Experience for Undergraduates at NU: Theoretical and computational Chemistry
%%- Purdue university: Computational nanotechnology

\end{document}
